\begin{thebibliography}{9}

\bibitem{trainpositioning}
J. Otegui, \textit{A Survey of Train Positioning Solutions, IEEE Sensors Journal, Vol. 17, No. 20 (2017)}

\bibitem{tecnicheodierne}
T. Albrecht et al, \textit{A precise and reliable train positioning system and its use for automation of train
operation, Proc. IEEE Int. Conf. Intell. Rail Transp. (2013)}

\bibitem{ertms}
European Commission, \textit{
	Delivering an effective and interoperable European Rail Traffic Management System
	(ERTMS) - the way ahead (2017)}

\bibitem{svolta}
J. Marais, J. Beugin, M. Berbineau, \textit{A Survey of GNSS-Based Research and
	Developments for the European Railway Signaling, IEEE transactions on intelligent transportation system (2017)}

\bibitem{etcs3}
A. Neri, F. Rispoli, P. Salvatori, \textit{An analytical assessment of
a GNSS-based train integrity solution in typical ERTMS level 3
scenarios, in Proc. Eur. Navigat. Conf. (ENC), Bordeaux, France, (2015)}

\bibitem{interlocking}
 P. Josserand, F.H Willard, \textit{Rights of Trains (5th ed.),Simmons-Boardman Publishing Corporation, New York (1957)}
 
\bibitem{marocchini}
N.A. Zafar et al, \textit{Towards the safety properties of moving blockrailway interlocking system, International Journal of Innovative Computing Information and Control (2012)}

\bibitem{MISRA}
MISRA, \textit{MISRA-C:2004, Guidelines for the use of the C language in critical systems (2004)}

\bibitem{sil}
International Electrotechnical Commission, \textit{61508-1: Functional safety of electrical/electronic/programmable electronic safety-related systems, edition 2.0 (2010)}


\bibitem{50128}
CENELEC European Committee for Electrotechnical Standardization. \textit{EN 50128:2011 - Railway Applications - Communications, signalling and processing systems - Software for railway control and protections systems (2011)}

\bibitem{market}
R. S. Hosse, H. Manz, K. Burmeister, E. Schnieder, \textit{Market
analysis for satellite train localisation for train control systems,
Proc. 5th Conf. Transp. Solutions Res. Deployment Transp. (2014)}
\bibitem{cps}
D. Basile et al, \textit{A Refinement Approach to Analyse Critical Cyber-Physical Systems,
Software Engineering and Formal Methods  (2017)}

\bibitem{cecca}
A. Ceccarelli et al, \emph{Basic Concepts on Systems of Systems, Cyber-Physical Systems of Systems, Springer (2017)}


\bibitem{sfarailway}
A. Mirabadi et al, \textit{Application of sensor fusion to railway systems, IEEE (1996)}

\bibitem{datafuse}
F. Bohringer, A. Geistler, \textit{Adaptation of the kinematic train
	model using the interacting multiple model estimator, Advances in
	Transport, vol. 74, no. 7. Southampton (2004)}

\bibitem{sfaimugps}
B. Cai, X. Wang, \textit{Train positioning via integration and
fusion of GPS and inertial sensors, WIT Transactions on the Built Environment, Southampton (2000)}

\bibitem{sfaimuodo}
M. Malvezzi et al, \textit{A localization algorithm for railway vehicles based on sensor fusion between tachometers and inertial measurement units, Proc. Inst. Mech.}

\bibitem{sfaimuodogps}
C. Reimer et al, \textit{INS/GNSS/odometer
data fusion in railway applications, Proc. DGON Intertial Sensors
Syst. (ISS), vol. 2. Karlsruhe, Germany (2016)} 

\bibitem{sqlite3}
L. Junyan et al, \textit{Application Research of Embedded Database SQLite, IEEE (2009)}

\bibitem{partialmeas}
X. Liu, A. Goldsmith, \textit{
Kalman  Filtering with Partial Observation Losses, Department of Electrical Engineering, Stanford University, Stanford, USA}

\bibitem{gpsdarkarea}
R. Mazl, L. Preucil, \textit{Sensor Data Fusion for Inertial Navigation of
Trains in GPS Dark Areas (Mathematics in Science and Engineering),
San Diego, CA, USA (2003)}

\bibitem{interfacespec}
H. Kopetz, \textit{Real-Time Systems: Design Principles for Distributed Embedded Applications 2nd edn, Springer, New York (2011)}

\bibitem{clock}
H. Kopetz, W. Ochsenreiter, \textit{Clock synchronization in distributed real-time systems, IEEE (1987)}

\bibitem{monitoring}
K. Wolter et al,
\textit{Resilience Assessment and Evaluation of Computing Systems, Springer (2012)}

\bibitem{timetriggered}
M.J. Pont, \emph{Patterns for Time-Triggered Embedded Systems, Addison-Wesley (2001)}

\bibitem{evttimetriggered}
H. Kopetz, \emph{Event-Triggered versus Time-Triggered Real-Time Systems, Springer (1991)}

\bibitem{libroreti}
ISO/IEC 7498-1:1994, \textit{
Information technology, Open Systems Interconnection - Basic Reference Model: The Basic Model (1994)}

\bibitem{librokalman}
D.E. Katlin, \textit{Estimation, Control, and the Discrete Kalman Filter, Applied Mathematical Science, Springer (1987)}

\bibitem{measnoise}
S. Dilhaire, D. Maillet, \textit{Dealing  with the measurement noise of a sensor (2015)}

\end{thebibliography}